
%-------------------------
% Resume in Latex
% Generated Automatically
%-------------------------

\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%----------HEADING (From Master Data)----------
\begin{center}
    {\Huge \scshape Rishit Epari} \\ \vspace{1pt}
    Philadelphia, PA, USA \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 737-500-7226 ~ \href{mailto:rishit.epari@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rishit.epari@gmail.com}} ~ 
    \href{https://linkedin.com/in/eparirishit}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/eparirishit}}  ~
    \href{https://github.com/eparirishit}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/eparirishit}}
\end{center}

%----------SUMMARY (Generated)----------
\section{Professional Summary}
Full Stack Engineer with 5 years of experience in AI infrastructure. Specialized in JavaScript, React, and TypeScript. Focused on developing scalable applications to pioneer distributed AI infrastructure.

%-----------EDUCATION (Static from Master Data)-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Drexel University}{Expected: 2026-05}
    {Master of Science in Computer Science | GPA: 3.85}{Philadelphia, PA}
    \resumeItemListStart
        \resumeItem{Focus: Artificial Intelligence, Machine Learning}
    \resumeItemListEnd

  \resumeSubheading
    {KIIT University}{2015}
    {Bachelor of Technology in Computer Science \& Engineering}{Bhubaneswar, India}
\resumeSubHeadingListEnd

%-----------EXPERIENCE (Generated)-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
          {Resolution Life}{Sep 2025 - Present}
          {AI Data Scientist (Co-op)}{Philadelphia, USA}
          \resumeItemListStart
            \resumeItem{Enhanced AI agent performance by refining prompts for low-quality interactions, raising response quality scores above defined evaluation thresholds.}
        \resumeItem{Architected an automated AI governance framework using Power Automate to trigger API-based audits for bias, risk, and quality metrics with real-time alerts.}
        \resumeItem{Engineered a custom multi-agent competitive analysis system using OpenAI APIs to autonomously evaluate competitor products and generate differentiation reports.}
          \resumeItemListEnd

    \resumeSubheading
          {mavQ}{Jun 2022 - Aug 2024}
          {Senior Software Development Engineer}{Hyderabad, India}
          \resumeItemListStart
            \resumeItem{Built scalable Spring Boot microservices supporting high-traffic customer deployments with resilient inter-service communication using Feign clients.}
        \resumeItem{Developed and deployed an IVR solution using AWS Lambda and Amazon Connect, automating airport helpdesk operations handling 200+ calls daily.}
        \resumeItem{Built and optimized ETL pipelines using Azure Data Factory to integrate APIs, SQL Server, and Blob storage into Salesforce.}
          \resumeItemListEnd

    \resumeSubheading
          {MTX}{Jul 2021 - Jun 2022}
          {Senior Consultant}{Hyderabad, India}
          \resumeItemListStart
            \resumeItem{Programmatically provisioned Azure resources in multi-tenant environments, reducing onboarding time by 70\%.}
        \resumeItem{Automated IIS deployments using Jenkins and Octopus Deploy, reducing manual errors and accelerating releases.}
        \resumeItem{Implemented SAML 2.0 integration with Component Space for SSO authentication, enhancing web application security.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS (Generated)-----------
\section{Select Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
              {\textbf{FactChecker} $|$ \emph{Python, FastAPI, Next.js}}{Apr 2025 - Jun 2025}
              \resumeItemListStart
            \resumeItem{Engineered an AI fact-checking platform using FastAPI and OpenAI API, integrating three parallel RAG pipelines for ensemble claim verification with web search retrieval.}
        \resumeItem{Implemented multi-stage hallucination detection using agreement gates and GPT-4o-powered stance classification to improve factual reliability.}
        \resumeItem{Built citation-backed explanation pipeline providing transparent evidence with source attribution and confidence scoring to increase trust in model outputs.}
              \resumeItemListEnd

      \resumeProjectHeading
              {\textbf{EcoMedAI} $|$ \emph{Python, FastAPI, LLM}}{Feb 2025 - Feb 2025}
              \resumeItemListStart
            \resumeItem{Developed a medical waste classification pipeline using fine-tuned ResNet50 trained on WHO medical datasets, processing 10k+ items/month to reduce hazardous disposal costs by 15\%.}
        \resumeItem{Architected a RAG-based recommendation engine using Gemini and FAISS for sustainable supply procurement, leveraging semantic search and LLM re-ranking.}
        \resumeItem{Implemented waste stream mapping system translating WHO categories into color-coded bin classifications, preventing costly misclassification.}
              \resumeItemListEnd

      \resumeProjectHeading
              {\textbf{CryptoSecure} $|$ \emph{React, Node.js, Claude Sonnet}}{Dec 2025 - Present}
              \resumeItemListStart
            \resumeItem{Architected an AI-powered security scanner for TON blockchain smart contracts, reducing audit time from weeks to under a minute.}
        \resumeItem{Developed vulnerability detection engine using LLMs to identify 8+ semantic defect types.}
        \resumeItem{Designed adversarial multi-agent framework to simulate exploit attempts, validating smart contract resilience against diverse attack vectors.}
              \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS (Generated)-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Core Competencies}{: JavaScript, TypeScript, React, WebSockets, PostgreSQL, GitLab CI/CD} \\
     \textbf{Languages \& Frameworks}{: HTML, CSS, Redux, Cypress} \\
     \textbf{DevOps \& Tools}{: AWS, Docker, Kubernetes, GitHub Actions} \\
    }}
 \end{itemize}

%-----------CERTIFICATIONS (Static)-----------
\section{Certifications}
AWS Certified Developer - Associate (Jul 2024) $|$ AWS Certified Cloud Practitioner (Jan 2024)

\end{document}
