%-------------------------
% Resume in Latex
% Author : Rishit Epari
% JOB LINK: https://careers-c1.icims.com/jobs/7038/data-engineer---c1-gov/job?mode=job&iis=SOURCE&iisn=LinkedInJobPosting&jr_id=68eb8d0676a1db7c59860d44
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% --- FIX: Force Bullets for both Levels ---
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}  % Level 1
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$} % Level 2

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% --- HEADER (Static or Dynamic based on your preference) ---
\begin{center}
    {\Huge \scshape Rishit Epari} \\ \vspace{1pt}
    Philadelphia, PA, USA \\ \vspace{1pt}
    \small
    \faPhone\ 737-500-7226 ~
    \href{mailto:rishit.epari@gmail.com}{\faEnvelope\ rishit.epari@gmail.com} ~
    \href{https://linkedin.com/in/eparirishit}{\faLinkedin\ linkedin.com/in/eparirishit} ~
    \href{https://github.com/eparirishit}{\faGithub\ github.com/eparirishit}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
\small{
Data Engineer with over 4 years of experience designing and optimizing scalable ETL/ELT pipelines across Azure and AWS platforms. Skilled in Python, SQL Server, Azure Data Factory and AWS Lambda, with a track record of cutting data processing times by 20\% and automating governance workflows. Proven ability to integrate diverse data sources and ensure data reliability for enterprise analytics.
}
\vspace{-10pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Drexel University}{Expected: May 2026}
    {Master of Science in Computer Science}{Philadelphia, PA}
    \resumeItemListStart
        \resumeItem{Concentration: Artificial Intelligence \& Machine Learning | GPA: 3.85}
    \resumeItemListEnd

  \resumeSubheading
    {KIIT University}{2015}
    {Bachelor of Technology in Computer Science \& Engineering}{Bhubaneswar, India}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {AI Data Scientist (Co-op)}{Sep 2025 -- Present}
    {Resolution Life}{Philadelphia, USA}
    \resumeItemListStart
        \resumeItem{Enhanced AI agent performance by refining prompts for the bottom 20\% of interactions in machine learning pipelines, raising response quality scores (via LLM-as-a-Judge) above the 80\% threshold.}
        \resumeItem{Architected an automated AI data governance framework using Power Automate to trigger API-based audits for bias, risk, and quality metrics with real-time alerts.}
        \resumeItem{Engineered a custom multi-agent competitive analysis system using OpenAI APIs to autonomously evaluate competitor products and generate differentiation reports.}
    \resumeItemListEnd

  \resumeSubheading
    {Senior Software Development Engineer}{Jun 2022 -- Aug 2024}
    {mavQ}{Hyderabad, India}
    \resumeItemListStart
        \resumeItem{Built scalable Spring Boot microservices supporting high-traffic customer deployments with resilient inter-service communication using Feign clients.}
        \resumeItem{Engineered real-time data sync between Salesforce and SQL Server via Azure Logic Apps, significantly reducing manual data reconciliation tasks.}
        \resumeItem{Built robust ETL pipelines in Azure Data Factory to integrate heterogeneous data sources (APIs, SQL Server) into centralized data warehouses, aligning with modern data architectures.}
    \resumeItemListEnd

  \resumeSubheading
    {Senior Consultant}{Jul 2021 -- Jun 2022}
    {MTX}{Hyderabad, India}
    \resumeItemListStart
        \resumeItem{Programmatically provisioned Azure resources (KeyVault, SQL, Blob Storage) in multi-tenant setups using infrastructure-as-code, slashing new-user onboarding time by 70\%.}
        \resumeItem{Automated IIS deployment using Jenkins and Octopus Deploy within CI/CD pipelines, reducing manual errors and boosting deployment speed for data applications.}
        \resumeItem{Optimized complex SQL queries within ETL workflows, cutting data processing time by 20\% and ensuring mapping accuracy for large-scale customer deployments.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{BillSplitter} $|$ \emph{Next.js, TypeScript, Tailwind, Gemini API}}{May 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Engineered an AI-powered receipt processing system integrating with Splitwise APIs for automated expense extraction.}
        \resumeItem{Integrated Google Gemini 2.5 Flash API for multimodal OCR to scan receipts, achieving 99.8\% extraction accuracy.}
        % \resumeItem{Built a full-stack TypeScript application using Next.js with React Server Components and responsive PWA capabilities.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{FactChecker} $|$ \emph{Python, FastAPI, Next.js, GCP, RAG}}{Apr 2025 -- Jun 2025}
    \resumeItemListStart
        \resumeItem{Engineered an AI fact-checking platform using FastAPI and OpenAI API, integrating three parallel RAG pipelines for ensemble claim verification with web search retrieval.}
        % \resumeItem{Implemented multi-stage hallucination detection using agreement gates and GPT-4o-powered stance classification to improve factual reliability.}
        \resumeItem{Built citation-backed explanation pipeline providing transparent evidence with source attribution and confidence scoring to increase trust in model outputs.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, SQL (T-SQL), C\#, Java} \\
    \textbf{Cloud \& DevOps}{: Azure (Data Factory, Logic Apps, SQL, DevOps), AWS (Lambda, S3, EC2 Connect), Docker, Kubernetes, Infrastructure-as-Code, CI/CD Pipelines} \\
    \textbf{Data Engineering}{: Data Pipeline Tools, Data Architecture, Data Modeling, Machine Learning Pipelines} \\
    \textbf{Data \& Databases}{: RDBMS, SQL Server, PostgreSQL, MySQL, ETL/ELT, Pandas, Numpy, Storage Engines} \\
  }}
\end{itemize}
\vspace{-10pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\small{
AWS Certified Developer – Associate (Jul 2024), AWS Certified Cloud Practitioner (Jan 2024)
}

\end{document}
