%-------------------------
% Resume in Latex
% Author : Rishit Epari
% JOB LINK: https://www.linkedin.com/jobs/view/4271774033/
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% --- FIX: Force Bullets for both Levels ---
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}  % Level 1
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$} % Level 2

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% --- HEADER (Static or Dynamic based on your preference) ---
\begin{center}
    {\Huge \scshape Rishit Epari} \\ \vspace{1pt}
    Philadelphia, PA, USA \\ \vspace{1pt}
    \small
    \faPhone\ 737-500-7226 ~
    \href{mailto:rishit.epari@gmail.com}{\faEnvelope\ rishit.epari@gmail.com} ~
    \href{https://linkedin.com/in/eparirishit}{\faLinkedin\ linkedin.com/in/eparirishit} ~
    \href{https://github.com/eparirishit}{\faGithub\ github.com/eparirishit}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
\small{
AI Data Scientist skilled in developing governance frameworks and conducting risk assessments for AI systems. Experienced in designing automated audits for bias, risk and quality, refining prompt performance, and engineering data pipelines across cloud platforms. Proven ability to collaborate with cross-functional teams to implement real-time compliance alerts and drive safe, ethical AI deployments.
}
\vspace{-10pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Drexel University}{Expected: May 2026}
    {Master of Science in Computer Science}{Philadelphia, PA}
    \resumeItemListStart
        \resumeItem{Concentration: Artificial Intelligence \& Machine Learning | GPA: 3.85}
    \resumeItemListEnd

  \resumeSubheading
    {KIIT University}{}
    {Bachelor of Technology in Computer Science \& Engineering}{Bhubaneswar, India}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {AI Data Scientist (Co-op)}{Sep 2025 -- Present}
    {Resolution Life}{Philadelphia, USA}
    \resumeItemListStart
        \resumeItem{Conducted data analysis to identify the bottom 20\% of AI agent interactions and refined prompts, raising response quality scores above 80\%.}
        \resumeItem{Architected an automated AI governance framework using Power Automate to audit new AI widgets for bias and risk, leveraging AI safety principles and triggering real-time compliance alerts.}
        \resumeItem{Engineered a multi-agent competitive analysis system that autonomously evaluates competitor products against in-house solutions and presents insights through interactive data visualizations.}
    \resumeItemListEnd

  \resumeSubheading
    {Senior Software Development Engineer}{Jun 2022 -- Aug 2024}
    {mavQ}{Hyderabad, India}
    \resumeItemListStart
        \resumeItem{Built ETL pipelines in Azure Data Factory to integrate data from APIs, SQL Server, and Blob storage into Salesforce, performing data analysis to validate data accuracy and integrity.}
        \resumeItem{Engineered real-time data sync between Salesforce and SQL Server via Logic Apps, reducing manual data tasks.}
        \resumeItem{Collaborated with cross-functional teams (data scientists, business analysts) to define and engineer data solutions, applying statistical methods to ensure robust data quality.}
    \resumeItemListEnd

  \resumeSubheading
    {Senior Consultant}{Jul 2021 -- Jun 2022}
    {MTX}{Hyderabad, India}
    \resumeItemListStart
        \resumeItem{Programmatically provisioned Azure resources in multi-tenant environments, reducing onboarding time by 70\%.}
        \resumeItem{Automated IIS deployments using Jenkins and Octopus Deploy, reducing manual errors and accelerating releases.}
        \resumeItem{Implemented SAML 2.0 integration with Component Space for SSO authentication, enhancing web application security.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{CryptoSecure} $|$ \emph{React, Node.js, Claude Sonnet, Tailwind}}{Dec 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Built a vulnerability detection engine using Claude Sonnet 4.5 to identify 8+ semantic defect types (reentrancy, overflow).}
        \resumeItem{Engineered an autonomous adversarial agent that orchestrates multiple LLMs to simulate exploit attempts, validating smart contract resilience against diverse attack vectors.}
    \resumeItemListEnd
  \resumeProjectHeading
    {\textbf{FactChecker} $|$ \emph{Python, FastAPI, Next.js, GCP, RAG}}{Apr 2025 -- Jun 2025}
    \resumeItemListStart
        \resumeItem{Engineered an AI fact-checking platform using FastAPI and OpenAI API, integrating three parallel RAG pipelines (RARR, FactCheckGPT, FacTool) for ensemble claim verification with web search retrieval.}
        \resumeItem{Implemented multi-stage hallucination detection using agreement gates and GPT-4o-powered stance classification to improve factual reliability.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
  \textbf{Programming Languages}{: Python, Java, C\#, SQL} \\
    \textbf{AI / Machine Learning}{: Python, PyTorch, TensorFlow, Scikit-learn, Pandas, NumPy, Matplotlib, Hugging Face, RAG, LLM Fine-tuning, FAISS} \\
    \textbf{Responsible AI \& Safety Practices}: {AI Safety, Risk Assessment, Adversarial Testing} \\
    \textbf{Cloud \& MLOps}{: Azure (ADF, Logic Apps, DevOps, SQL, Functions), AWS (Lambda, DynamoDB, EC2, CloudWatch, S3), Docker, Kubernetes, Git/GitHub, GitHub Actions} \\
    \textbf{Data Management \& Analysis}{: SQL Server, PostgreSQL, MySQL, Data Analysis, Data Visualizations} \\
  }}
\end{itemize}
\vspace{-10pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\small{
AWS Certified Developer – Associate (Jul 2024), AWS Certified Cloud Practitioner (Jan 2024)
}

\end{document}
