%-------------------------
% Resume in Latex
% Author : Rishit Epari
% JOB LINK: https://fa-euxc-saasfaprod1.fa.ocs.oraclecloud.com/hcmUI/CandidateExperience/en/sites/CX_1/job/11922?utm_medium=jobboard&utm_source=jobright
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% --- FIX: Force Bullets for both Levels ---
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}  % Level 1
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$} % Level 2

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% --- HEADER (Static or Dynamic based on your preference) ---
\begin{center}
    {\Huge \scshape Rishit Epari } \\ \vspace{1pt}
    Philadelphia, PA, USA \\ \vspace{1pt}
    \small
    \faPhone\ 737-500-7226 ~
    \href{mailto:rishit.epari@gmail.com}{\faEnvelope\ rishit.epari@gmail.com} ~
    \href{ https://linkedin.com/in/eparirishit }{\faLinkedin\ linkedin.com/in/eparirishit} ~
    \href{ https://github.com/eparirishit }{\faGithub\ github.com/eparirishit}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
\small{
Computer Science master’s student with over 2 years of experience developing data-focused applications. Skilled in Python scripting, SQL query optimization, and building ETL pipelines on Azure and AWS. Proven ability to streamline data processes—reducing processing time by 20\%—and collaborate across teams to deliver reliable solutions in fast-paced IT environments.
}
\vspace{-10pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Drexel University}{Expected: May 2026}
    {Master of Science in Computer Science}{Philadelphia, PA}
    \resumeItemListStart
        \resumeItem{Concentration: Artificial Intelligence \& Machine Learning | GPA: 3.85}
    \resumeItemListEnd

  \resumeSubheading
    {KIIT University}{}
    {Bachelor of Technology in Computer Science \& Engineering}{Bhubaneswar, India}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {AI Data Scientist (Co-op)}{Sep 2025 -- Present}
    {Resolution Life}{Philadelphia, USA}
    \resumeItemListStart
        \resumeItem{Enhanced machine learning agent performance by refining prompts for the bottom 20\% of interactions, raising response quality scores above the 80\% threshold.}
        \resumeItem{Architected an automated AI governance framework using Power Automate and design patterns to audit new AI widgets for bias, risk, and quality metrics, triggering real-time compliance alerts.}
        \resumeItem{Engineered a Python-based multi-agent competitive analysis system for data processing that autonomously evaluates competitor products against in-house solutions, generating strategic differentiation reports.}
    \resumeItemListEnd

  \resumeSubheading
    {Senior Software Development Engineer}{Jun 2022 -- Aug 2024}
    {mavQ}{Hyderabad, India}
    \resumeItemListStart
        \resumeItem{Built Python-based ETL pipelines in Azure Data Factory to integrate data from APIs, SQL Server, and Blob storage into Salesforce.}
        \resumeItem{Collaborated with cross-functional teams (data scientists, business analysts) to define and engineer data solutions using Git for version control.}
        \resumeItem{Developed and deployed an IVR solution using AWS Lambda and Amazon Connect, automating airport helpdesk operations handling 200+ calls daily.}
    \resumeItemListEnd

  % \resumeSubheading
  %   {Senior Consultant}{Jul 2021 -- Jun 2022}
  %   {MTX}{Hyderabad, India}
  %   \resumeItemListStart
  %       \resumeItem{Programmatically provisioned Azure resources in multi-tenant environments, reducing onboarding time by 70\%.}
  %       \resumeItem{Automated IIS deployments using Jenkins and Octopus Deploy, reducing manual errors and accelerating releases.}
  %       \resumeItem{Implemented SAML 2.0 integration with Component Space for SSO authentication, enhancing web application security.}
  %   \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{CryptoSecure} $|$ \emph{React, Node.js, Claude Sonnet, Tailwind}}{Dec 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Architected an AI-powered security scanner for TON blockchain smart contracts, reducing audit time from weeks to under a minute.}
        \resumeItem{Built a vulnerability detection engine using Claude Sonnet 4.5 to identify 8+ semantic defect types (reentrancy, overflow).}
        \resumeItem{Engineered an autonomous adversarial agent that orchestrates multiple LLMs to simulate exploit attempts, validating smart contract resilience against diverse attack vectors.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{FactChecker} $|$ \emph{Python, FastAPI, Next.js, GCP, RAG}}{Apr 2025 -- Jun 2025}
    \resumeItemListStart
        \resumeItem{Engineered an AI fact-checking platform using FastAPI and OpenAI API, integrating three parallel RAG pipelines (RARR, FactCheckGPT, FacTool) for ensemble claim verification with web search retrieval.}
        \resumeItem{Implemented multi-stage hallucination detection using agreement gates and GPT-4o-powered stance classification to improve factual reliability.}
        \resumeItem{Built citation-backed explanation pipeline providing transparent evidence with source attribution and confidence scoring to increase trust in model outputs.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
  \textbf{Programming Languages}{: Python, Java, C\#, SQL} \\
    \textbf{AI / ML Libraries \& Frameworks}{: PyTorch, TensorFlow, Scikit-learn, Pandas, NumPy, Matplotlib, Hugging Face, RAG, Machine Learning} \\
    \textbf{Web Technologies}: {REST APIs, FastAPI, Next.js, React} \\
    \textbf{Cloud \& MLOps}{: AWS, Azure, GCP, Docker, Kubernetes, Git/GitHub, GitHub Actions, Design Patterns} \\
    \textbf{Database \& Data Processing}{: SQL Server, PostgreSQL, MySQL, Data Analysis, Data Visualizations} \\
  }}
\end{itemize}
\vspace{-10pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\small{
AWS Certified Developer – Associate (Jul 2024), AWS Certified Cloud Practitioner (Jan 2024)
}

\end{document}
